Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification

### 2019-07-30 190410_Paper_ACPR/paper_v3.tex
acpr2019: submit

Recently, the commercial Wi-Fi device is also proposed to be utilized as a in-air signature acquisition sensor due to its easy accessible property \cite{moon2017air}. By capturing the Wi-Fi CSI signal to observe the distinctive motions, the Wi-Fi based in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}. However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Components Analysis. Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data, more recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal based user authentication systems for the better verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.

@@

\section{Related Works}

\subsection{Triplet Network}
% triplet network
Triplet network is kind of a metric learning model \cite{weinberger2006distance} which aims to learn useful representations by using the distance comparison \cite{hoffer2015deep}. It is widely used in person re-identification problems, which solves the matching problem of individuals and identity between camera images\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}. 
The distinction between classes is challenging in this task since the distinctive feature is relatively weak compare to the background features such as pose, hair and textures.

@@

% Rel works: KAR learning
\subsection{Kernel and the Range space learning}\label{kar}

The multilayer feedforward neural networks is generally trained by the gradient descent method and the backpropagation.
However, setting the learning parameters such as learning rate or momentum value is important to use the gradient descent method.

@@

%% Methods
\section{Proposed System}

@@

% Figure 1
\begin{figure}
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v4}
    \caption{An overview of the proposed system} \label{fig1}
\end{figure}

@@

% Methods: ConvNets
\subsection{ConvNet Structures}

@@

% Dataset
\subsection{Dataset}
 In order to evaluate the verification performance of the proposed system, the Wi-Fi CSI signature dataset \cite{moon2017air} with single position was utilized in our experiments. After adopting the data preprocessing process proposed in \cite{moon2017air}, the Wi-Fi CSI signature dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 10 samples $\times$ 50 identities) with the sample size of 500 $\times$ 30 $\times$ 6. We utilized only the absolute value from each complex CSI signal in our experiments since the 2.4Ghz Wi-Fi CSI signals has device firmware issues in their phase signal~\cite{wang2015understanding}.

\subsection{Experimental Settings}

\subsubsection{Performance Evaluation}
The proposed system is evaluated under two cases: i) case I on comparison of the proposed system with other linear methods and deep learning based methods based on verification accuracy, and case II on detailed comparison with the deep learning based methods using receiver operating characteristic (ROC) curve and training loss curve. For the Case I, existing linear methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel function and total error rate minimization which adopts the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between} and deep learning based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking. The Siamese network and baseline triplet network utilized same ConvNet structures with the proposed system and only differed in the input data style and the loss function.

@@

\subsubsection{Network Structure and Parameter Settings}
The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}. With an input data size of 500 $\times$ 30 $\times$ 6, we set two network layers where the size of the each layer is 1024 and 16, respectively. Each layer is initialized with uniform distribution over [0, 1). We used ${tan}^{-1}$ as an activation function following \cite{toh2018analytic}.

\begin{table}[]
    \caption{The network structure of KAR space learning}\label{tab2}
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    Layer   & Size     & Activation \\ \hline
    Input   & 500x30x6 &            \\
    Fully-Connected 1 & 1x1x1024 & ArcTan     \\
    Fully-Connected 2 & 1x1x16  & ArcTan     \\
    Output  & 1x1x50   &            \\ \hline
    \end{tabular}
\end{table}

@@

 \begin{table}[]
    \caption{
        The structure of ConvNet model. For the convolution layer, kernel is specified as (m$\times$m) sized filter $\times$ \# of filters / \# of stride. For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride. The input sizes are denoted as rows $\times$ cols $\times$ \# of filters. 
    }\label{tab1}
    \centering
    \begin{tabular}{|c|c|c|c|}
    \hline
    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
    Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500x30x6   \\
    MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
    Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
    MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
    Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
    MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
    Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
    L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
    Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
    \end{tabular}
\end{table}

\subsection{Results and Discussion}

@@

\begin{table}[!h]
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signal dataset.}\label{tab3}
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
    Methology   &   Best EER (\%) &   Condition   \\  \hline
    LSE &   48.44   &  - \\ 
    PCA-LSE    &   30.79   &  Reduced dimension=40    \\
    SVM (Linear) &   28.23   &   c=1 \\
    SVM (RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
    Siamese network  &   23.53   &   lr=0.00005  \\
    Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
     \hline
    \end{tabular}
\end{table}

Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning based methods. As shown in the Fig.~\ref{fig2}(b), the proposed system clearly shows the largest AUC among three compared methods where other two methods showed similar AUC. Moreover in Fig.\ref{fig2}(b) which illustrates the training loss curve along the number of training iteration, the proposed system shows the fastest training loss convergence followed by the baseline triplet network. We note here that the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has difference starting value based on their function. According to these two observations, it can be concluded that the triplet input mining with KAR space learning not only improves the training loss convergence speed but also improves the verification performance.

% Figure 2,3
\begin{figure}[!h]
    \begin{center}
    \subfigure[][ROC Curve]{
         \includegraphics[height=6.4cm]{fig_roc_v9.eps}}
    \subfigure[][Training Loss Curve]{
         \includegraphics[height=6.4cm]{normalized_loss_curve_ma30_v1.eps}}
    \caption{(a) shows Receiver Operating Characteristic(ROC) Curve
    (b) shows Normalized Training Loss Curve of the Proposed System }
    \label{fig2}
    \end{center}
 \end{figure}

 % merged 2 graph: omitted separated graph
 \iffalse
 % Figure 3
 \begin{figure}[!h]
     \includegraphics[width=\textwidth]{fig_roc_v5.eps}
     \caption{Receiver Operating Characteristic(ROC) Curve of the Proposed System} \label{fig3}
 \end{figure}

 % Figure 2
     \begin{figure}[!h]
     \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v1.eps}
     \caption{Training Loss Curve of the Proposed System} \label{fig2}
 \end{figure}
 \fi

>>>>

Recently, the commercial Wi-Fi device is also proposed to be utilized as a in-air signature acquisition sensor due to its easy accessible property \cite{moon2017air}. By capturing the Wi-Fi CSI signal to observe the distinctive motions, the Wi-Fi based in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}. However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Component Analysis. Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data, more recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal based user authentication systems for the better verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.

@@

\section{Related works}

\subsection{Triplet network}
% triplet network
Triplet network is kind of a metric learning model \cite{weinberger2006distance} which aims to learn useful representations by using the distance comparison \cite{hoffer2015deep}. It is widely used in person re-identification problems, which solves the matching problem of individuals and identity between camera images\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}. 
The distinction between classes is challenging in this task since the distinctive feature is relatively weak compare to the background features such as pose, hair and textures.

@@

% Rel works: KAR learning
\subsection{Kernel and the range space learning}\label{kar}

The multilayer feedforward neural networks is generally trained by the gradient descent method and the backpropagation \cite{goodfellow2016deep}.
However, setting the learning parameters such as learning rate or momentum value is important to use the gradient descent method.

@@

%% Methods
\section{Proposed system}

@@

% Figure 1
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v5}
    \caption{An overview of the proposed system.} \label{fig1}
\end{figure}

@@

% Methods: ConvNets
\subsection{ConvNet structures}

@@

% Dataset
\subsection{Dataset}
 In order to evaluate the verification performance of the proposed system, the Wi-Fi CSI signature dataset \cite{moon2017air} with single position was utilized in our experiments. After adopting the data preprocessing process proposed in \cite{moon2017air}, the Wi-Fi CSI signature dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 10 samples $\times$ 50 identities) with the sample size of 500$\times$30$\times$6. We utilized only the absolute value from each complex CSI signal in our experiments since the 2.4Ghz Wi-Fi CSI signals has device firmware issues in their phase signal~\cite{wang2015understanding}.

\subsection{Experimental settings}

\subsubsection{Performance evaluation}
The proposed system is evaluated under two cases: i) case I on comparison of the proposed system with other linear methods and deep learning based methods based on verification accuracy, and case II on detailed comparison with the deep learning based methods using receiver operating characteristic (ROC) curve and training loss curve. For the Case I, existing linear methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel function and total error rate minimization which adopts the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between} and deep learning based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking. The Siamese network and baseline triplet network utilized same ConvNet structures with the proposed system and only differed in the input data style and the loss function.

@@

\subsubsection{Network Structure and Parameter Settings}
The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}. With an input data size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively. Each layer is initialized with uniform distribution over [0, 1). We used $\sigma = {tan}^{-1}$ as an activation function following \cite{toh2018analytic}.

\begin{table}[]
    \caption{The network structure of the KAR space learning.}\label{tab2}
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    Layer   & Size     & Activation \\ \hline
    Input   & 500$\times$30$\times$6 &            \\
    Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
    Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
    Output  & 1$\times$1$\times$50   &            \\ \hline
    \end{tabular}
\end{table}

@@

 \begin{table}[]
    \caption{
        The structure of ConvNet model. For the convolution layer, kernel is specified as (m$\times$m) sized filter $\times$ \# of filters / \# of stride. For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride. The input sizes are denoted as rows $\times$ cols $\times$ \# of filters. 
    }\label{tab1}
    \centering
    \begin{tabular}{|c|c|c|c|}
    \hline
    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
    Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
    MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
    Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
    MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
    Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
    MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
    Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
    L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
    Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
    \end{tabular}
\end{table}

\subsection{Results and discussion}

@@

\begin{table}[!h]
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signature dataset.}\label{tab3}
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
    Methology   &   Best EER (\%) &   Condition   \\  \hline
    LSE &   48.44   &  - \\ 
    PCA-LSE    &   30.79   &  Reduced dimension=40    \\
    SVM (Linear) &   28.23   &   c=1 \\
    SVM (RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
    Siamese network  &   23.53   &   lr=0.00005  \\
    Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
     \hline
    \end{tabular}
\end{table}

Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning based methods. As shown in the Fig.~\ref{fig2}(b), the proposed system clearly shows the largest Area Under Curve (AUC) among three compared methods where other two methods showed similar AUC. Moreover in Fig.\ref{fig2}(b) which illustrates the training loss curve along the number of training iteration, the proposed system shows the fastest training loss convergence followed by the baseline triplet network. We note here that the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has difference starting value based on their function. According to these two observations, it can be concluded that the triplet input mining with KAR space learning not only improves the training loss convergence speed but also improves the verification performance.

% Figure 2,3
\begin{figure}[!ht]
    \begin{center}
    \subfigure[][ROC Curve]{
        \includegraphics[height=6.4cm]{fig_roc_v11.eps}}
    \subfigure[][Normalized training loss curve]{
        \includegraphics[height=6.4cm]{normalized_loss_curve_ma30_v2.eps}}
    \caption{(a) shows the Receiver Operating Characteristic(ROC) Curve and 
    (b) shows the normalized training loss curve of the deep learning based methods. }
    \label{fig2}
    \end{center}
 \end{figure}

### 2019-07-30 190410_Paper_ACPR/paper_v4.tex
acpr2019: submit

\begin{document}
%
\title{Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification}
%
\titlerunning{Triplet Network adopting KAR Learning for Wi-Fi Signature Verification}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Young-Woong Kwon \and Jooyoung Kim \and Kar-Ann Toh}
%
\authorrunning{Y. Kwon et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
School of Electrical and Electronic Engineering, Yonsei University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of Korea\\
\email{\{herokwon, harrykim, katoh\}@yonsei.ac.kr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 15--250 words.
In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signals using a triplet network. 
To refine the triplet inputs for faster loss convergence, the kernel and the range space learning is adopted to mine the distinctive triple inputs from the training set of Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.

@@

In recent years, several behavioral biometric traits for identity authentication are investigated since they are free from the physical characteristic which user owns~\cite{bailador2011analysis}. Among the behavioral biometrics, the signature based user authentication~\cite{galbally2015line,sanmorino2012survey} is taking considerable interest with the development of the in-air signature recognition systems~\cite{galbally2015line,jeon2012system,malik20183dairsig}. 
With the help of sensors such as a depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition systems could have less spatial limitation in the signature acquisition process compare to other contact-based authentication systems.

Recently, the commercial Wi-Fi device is also proposed to be utilized as a in-air signature acquisition sensor due to its easy accessible property \cite{moon2017air}. By capturing the Wi-Fi CSI signal to observe the distinctive motions, the Wi-Fi based in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}. However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Component Analysis. Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data, more recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal based user authentication systems for the better verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.

In this paper, we utilize the deep triplet network for identity verification based on Wi-Fi CSI signature signal. To achieve not only the promising verification accuracy but also the fast training loss convergence speed for the commercial use, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} to mine the distinctive triplet inputs for training the triplet network. Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained using the mined triplet inputs based on L-2 distance comparison.
The main contributions of our work can be summarized as follows:
\begin{itemize}
\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using deep triplet network.
\item Adopted the KAR space learning to mine the distinctive triplet inputs which boosted the convergence speed of the training loss in triplet network.
\item Provision of the experimental study on an in-house Wi-Fi handwritten signature signal dataset collected from 50 subjects.
\end{itemize}

The paper is organized as follows: the related works including triplet network and KAR space learning will be introduced in Section 2 for immediate reference. Our proposed method will be discussed in Section 3. Section 4 describes our experimental results and analysis. Some concluding remarks will be followed in Section 5.

@@

\section{Conclusion}
In this paper, we proposed an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using triplet network adopting the kernel and the range (KAR) space learning. 
The kernel and the range space learning is initially adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compare to the basic triplet network and the Siamese network.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
%\bibliographystyle{splncs04}
%\bibliography{mybibliography}
%

>>>>

\begin{document}
%
\title{Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification}
%
\titlerunning{Triplet Network adopting KAR Learning for Wi-Fi Signature Verification}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Young-Woong Kwon \and Jooyoung Kim \and Kar-Ann Toh}
%
\authorrunning{Y. Kwon et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
School of Electrical and Electronic Engineering, Yonsei University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of Korea\\
\email{\{herokwon, harrykim, katoh\}@yonsei.ac.kr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 15--250 words.
In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signals using a triplet network. 
To refine the triplet inputs for fast loss convergence, the kernel and the range space learning is adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.

@@

In recent years, several behavioral biometric traits for identity authentication have been investigated in view of their rigid physical body independence~\cite{bailador2011analysis}. Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is taking considerable interest with the development of the in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}. % more in-air ref
With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than contact-based authentication systems.

Recently, the commercial Wi-Fi device has been adopted for in-air signature authentication due to its easy accessible property \cite{moon2017air}. Based on the distortion of the  Wi-Fi CSI signal according to the user gestures, the in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}. 
% omitted
%However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Component Analysis. Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data, 
More recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal based user authentication systems to improve the verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.

In this paper, we utilize the deep triplet network for identity verification based on Wi-Fi CSI signature signal. To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} to mine the distinctive triplet inputs. Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained based on L-2 distance comparison.

The main contributions of our work can be summarized as follows:
\begin{itemize}
\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
\item Adopted the KAR space learning to mine the distinctive triplet inputs which boosted the convergence speed of the training loss in triplet network.
\item Provision of the experimental study on an in-house Wi-Fi handwritten signature signal dataset collected from 50 subjects.
\end{itemize}

The paper is organized as follows: related works including the triplet network and KAR space learning will be introduced in Section 2 for immediate reference. Our proposed method will be discussed in Section 3. Section 4 describes our experimental results and analysis. Some concluding remarks will be given in Section 5.

@@

\section{Conclusion}
In this paper, we proposed an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using a triplet network adopting the kernel and the range (KAR) space learning. 
The kernel and the range space learning was initially adopted to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compared with the basic triplet network and the Siamese network.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
%\bibliographystyle{splncs04}
%\bibliography{mybibliography}
%
